The imprint of global magma oceans on exoplanet demographics

### 2023-02-23 src/tex/ms.tex
defend stellar age distribution

\subsubsection{Stellar luminosity tracks}
    Planetary systems are hosted by stars of a wide range of ages, and stellar luminosities evolve with time.
    Since the emergence of a runaway greenhouse phase on a planet is highly dependent on the level of radiation it receives, and thus on the luminosity of the host star, we assigned age-dependent luminosities to our synthetic stars.
    Stellar ages are notoriously poor-constrained (CITE); we thus drew random ages from a uniform distribution from \SI{0}{\giga\year} to \SI{10}{\giga\year}.
    We then assigned each star a luminosity from the mass-dependent evolutionary models in \citet{Baraffe1998}.
    Figure~\ref{fig:luminosity_tracks} shows the corresponding luminosity evolution as a function of stellar mass and age.
\begin{figure}[ht!]
    \script{plot_luminosity_tracks.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/luminosity_tracks.pdf}
        \caption{
            Bolometric luminosity tracks of stars with different masses, computed from stellar evolution models in \citet{Baraffe1998}.
            Low-mass stars, which make up the majority of stars in the solar neighborhood, undergo an extended early phase of several magnitudes higher luminosity before entering a lifetime of relative faintness.
        }
        \label{fig:luminosity_tracks}
    \end{centering}
\end{figure}

>>>>

\subsubsection{Stellar luminosity evolution}
Planetary systems are hosted by stars of a wide range of ages, and stellar luminosities evolve with time.
Since the emergence of a runaway greenhouse phase on a planet is highly dependent on the level of radiation it receives, and thus on the luminosity of the host star, we assigned age-dependent luminosities to our synthetic stars.

While stellar ages are notoriously poor-constrained~\cite[e.g.,][]{Adams2005}, the age distribution of planet host stars in the Solar neighborhood was shown to be broadly consistent with uniform~\citep{Reid2007,Gaidos2023}.
For our synthetic stars, we thus drew random ages from a uniform distribution from \SI{0}{\giga\year} to \SI{10}{\giga\year}.
We then assigned each star a luminosity from the mass-dependent evolutionary models in \citet{Baraffe1998}.
Figure~\ref{fig:luminosity_tracks} shows the corresponding luminosity evolution as a function of stellar mass and age.
\begin{figure}[ht!]
    \script{plot_luminosity_tracks.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/luminosity_tracks.pdf}
        \caption{
            Bolometric luminosity tracks of stars with different masses, computed from stellar evolution models in \citet{Baraffe1998}.
            Low-mass stars, which make up the majority of stars in the solar neighborhood, undergo an extended early phase of several magnitudes higher luminosity before entering a lifetime of relative faintness.
        }
        \label{fig:luminosity_tracks}
    \end{centering}
\end{figure}
